Capstone Movielens Report

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Temp commit.

####### endpoint.min_diff = 0
\
Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the [Details](#func.model.tune.param_range.details) section below).

@@

###### Details {#func.model.tune.param_range.details}
\
During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.

>>>>

####### endpoint.min_diff = 0
\
Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section below).

@@

::: Details {#func.model.tune.param_range.details }

During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
:::

###### Details
\

(ref:foo) During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.

###### Value
\
See the `Details`section [above](#func.model.tune.param_range.details). 
See the `Details`section [above](ref:foo). 
See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range). 
pdf_document2

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Temp commit.

\hfill\break
Defines the sensitivity threshold for determining the neighborhood
boundaries of the minimum \texttt{RMSE} value (for details, see the
\hyperref[func.model.tune.param_range.details]{Details} section below).

@@

@@

\hfill\break
During execution, the function uses a helper function specified by the
\texttt{fn\_tune.test.param\_value} parameter, which calculates the
\texttt{RMSE} value for the given parameter from the list determined by
the inner \texttt{param\_values} sequence.

>>>>

\hfill\break
Defines the sensitivity threshold for determining the neighborhood
boundaries of the minimum \texttt{RMSE} value (for details, see the
\texttt{Details} section below).

@@

::: Details \{\#func.model.tune.param\_range.details \}

During execution, the function uses a helper function specified by the
\texttt{fn\_tune.test.param\_value} parameter, which calculates the
\texttt{RMSE} value for the given parameter from the list determined by
the inner \texttt{param\_values} sequence. :::

@@

(ref:foo) During execution, the function uses a helper function
specified by the \texttt{fn\_tune.test.param\_value} parameter, which
calculates the \texttt{RMSE} value for the given parameter from the list
determined by the inner \texttt{param\_values} sequence.

\hfill\break
See the \texttt{Details}section
\hyperref[func.model.tune.param_range.details]{above}. See the
\texttt{Details}section \href{ref:foo}{above}. See the
\texttt{func.model.tune.param\_range} Function description
\hyperref[func.model.tune.param_range]{above}. pdf\_document2
